---
title: "RStudio Table Contest"
author: "Sam Parmar"
github: www.github.com/parmsam
date: "10/3/2020"
output: 
  html_document:
    toc: true
    theme: simplex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DT)
library(RColorBrewer)
library(sessioninfo)
```

```{css, echo=FALSE}
.header-section-number::after {
  content: ".";
}
```
# Background
The work here was created for the [2020 Rstudio Table Contest](https://blog.rstudio.com/2020/09/15/announcing-the-2020-rstudio-table-contest/). The code provided was used to develop an interactive table in an interactive HTML page using R markdown. The interactive table below takes advantage of the following features from the [DT package](https://rstudio.github.io/DT/):

* cell background coloring 
* cell color bars
* bold column font
* copy and download buttons
* number entries dropdown menu for user selection
* term search feature
* column filters
* column reordering
* responsive table to handle window resize

The [DT](https://rstudio.github.io/DT/), [Tidyverse](https://www.tidyverse.org/), and [RColorBrewer](https://cran.r-project.org/web/packages/RColorBrewer/RColorBrewer.pdf) packages were used.

# Code
```{r cars}
colorBars <- function(df, column, color) {
  df1 <- df %>% formatStyle(column,
  background = styleColorBar(range(mpg[column]), color),
  backgroundSize = '100% 50%',
  backgroundRepeat = 'no-repeat',
  backgroundPosition = 'center')
  return(df1)
}
  
table <- mpg %>% 
  datatable(selection = "single", extensions=c("Buttons","ColReorder", "Responsive"), 
            filter = list(position = 'top', clear = FALSE, plain = TRUE), 
            class = 'cell-border stripe',
    options=list(searchHighlight= FALSE, pagelength =5, lengthMenu = list(c(10, 20, 50, -1),c("10","20","50","All")), hover=TRUE,
                 dom='tlfrtBip', colReorder = TRUE, keys=TRUE,
                 columnDefs = list(list(searchable = FALSE)),
                 fixedColumns = TRUE,
                buttons= list('copy', list(textAlign='center',
        extend = 'collection',
        buttons = list(list(extend='csv',filename='mpg_summary'), list(extend='excel',filename='mpg_summary')),
        text = 'Download'
      )),
                 list(colReorder = TRUE)
                 )) %>% 
colorBars("displ", 'lightblue') %>%
colorBars("hwy", 'coral') %>%
colorBars("cyl", 'orange') %>%
colorBars("cty", 'lightgreen') %>% 
formatStyle('manufacturer', fontWeight = 'bold',color='black',textAlign = 'center',
     backgroundColor = styleEqual(unique(mpg$manufacturer), colorRampPalette(c('#d75027','#f46d43','#fdae61','#fee08b','#ffffbf','#d9ef8b','#a6d96a','#66bd63','#1a9850','#006837' ))(n_distinct(mpg$manufacturer)))
  )
```

# Table
```{r echo=FALSE}
table
```

# Sources
The following sources were consulted in building this submission.

* https://rstudio.github.io/DT/
* https://www.youtube.com/watch?v=yott4quKN6s&ab_channel=LanderAnalytics
* https://stackoverflow.com/questions/53265769/dtdatatables-generated-html-table-shows-display-anomalies-missing-character
* https://data-se.netlify.app/2019/01/14/a-clean-sessioninfo-page/

# Source code
* Github repo [here](https://github.com/parmsam/rstudio-table-contest)

# Session Info
```{r echo=FALSE}
si <- session_info()
pl <- map2(si$packages$package, 
              si$packages$loadedversion,
     ~ paste0(.x, " ", .y)) %>% 
  simplify()

```
- OS: `r si$platform$os`
- Version: `r si$platform$version`
- Date: `r si$platform$date`
- Packages: `r pl`
